---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a) [Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler - Cem Vardar & Erdi Dasdemir](https://www.youtube.com/watch?v=Fi8-phj1X1A)

Mr. Vardar, an experienced industrial engineer and data scientist, discusses how data science and industrial engineering integrated with each other, emphasizing that data analytics is a key problem-solving tool.

He highlights that simple solutions are often the most effective in complex systems. While complexity may be necessary, solutions should start with a structured, simple approach.

Mr. Vardar also explains various data science roles, their responsibilities, and the essential skills needed in the field. He introduces the Pareto Principle (80-20 rule), suggesting that learning just 20% of key skills (like SQL, programming, and data visualization) can meet 80% of an industrial engineer’s needs.

The talk concludes with career advice, book recommendations, and an interactive Q&A session on industry trends and best practices.

## (b) Explore Statistical Summaries with Custom Functions and Iteration Methods

```         
$mean [1] 20.09062  $median [1] 19.2  $variance [1] 36.3241  $IQR [1] 7.375  $minimum [1] 10.4  $maximum [1] 33.9 
```

```         
Statistics for mpg : $mean [1] 20.09062  $median [1] 19.2  $variance [1] 36.3241  $IQR [1] 7.375  $minimum [1] 10.4  $maximum [1] 33.9   Statistics for cyl : $mean [1] 6.1875  $median [1] 6  $variance [1] 3.189516  $IQR [1] 4  $minimum [1] 4  $maximum [1] 8   Statistics for disp : $mean [1] 230.7219  $median [1] 196.3  $variance [1] 15360.8  $IQR [1] 205.175  $minimum [1] 71.1  $maximum [1] 472   Statistics for hp : $mean [1] 146.6875  $median [1] 123  $variance [1] 4700.867  $IQR [1] 83.5  $minimum [1] 52  $maximum [1] 335   Statistics for drat : $mean [1] 3.596563  $median [1] 3.695  $variance [1] 0.2858814  $IQR [1] 0.84  $minimum [1] 2.76  $maximum [1] 4.93   Statistics for wt : $mean [1] 3.21725  $median [1] 3.325  $variance [1] 0.957379  $IQR [1] 1.02875  $minimum [1] 1.513  $maximum [1] 5.424   Statistics for qsec : $mean [1] 17.84875  $median [1] 17.71  $variance [1] 3.193166  $IQR [1] 2.0075  $minimum [1] 14.5  $maximum [1] 22.9   Statistics for vs : $mean [1] 0.4375  $median [1] 0  $variance [1] 0.2540323  $IQR [1] 1  $minimum [1] 0  $maximum [1] 1   Statistics for am : $mean [1] 0.40625  $median [1] 0  $variance [1] 0.2489919  $IQR [1] 1  $minimum [1] 0  $maximum [1] 1   Statistics for gear : $mean [1] 3.6875  $median [1] 4  $variance [1] 0.5443548  $IQR [1] 1  $minimum [1] 3  $maximum [1] 5   Statistics for carb : $mean [1] 2.8125  $median [1] 2  $variance [1] 2.608871  $IQR [1] 2  $minimum [1] 1  $maximum [1] 8 
```

```         
 mpg      cyl      disp     hp       drat      wt       qsec     mean     20.09062 6.1875   230.7219 146.6875 3.596563  3.21725  17.84875 median   19.2     6        196.3    123      3.695     3.325    17.71    variance 36.3241  3.189516 15360.8  4700.867 0.2858814 0.957379 3.193166 IQR      7.375    4        205.175  83.5     0.84      1.02875  2.0075   minimum  10.4     4        71.1     52       2.76      1.513    14.5     maximum  33.9     8        472      335      4.93      5.424    22.9              vs        am        gear      carb     mean     0.4375    0.40625   3.6875    2.8125   median   0         0         4         2        variance 0.2540323 0.2489919 0.5443548 2.608871 IQR      1         1         1         2        minimum  0         0         3         1        maximum  1         1         5         8       
```

## (c) Load the “na_example” dataset from the dslabs package

```{r}
library(dslabs)

data(na_example)

print("Original Dataset with NAs:")
print(na_example)
```


